---
title: "Project 4"
author: "Vivian Kong"
date: "11/13/2016"
output:
  html_document: default
  pdf_document: default
---

## Install Neo4j


## Connect to MySQL database, I will use the flight database
```{r}
library(RMySQL)
mydb <- dbConnect(MySQL(), user = 'root', password = '081465zN', host = 'localhost', dbname='flight')
```

## pull out the tables and disconnet to MySQL after we finish importing
```{r}
airlines <- dbReadTable(mydb, "airlines")
airports <- dbReadTable(mydb, "airports")
flights <- dbReadTable(mydb, "flights")
planes <-dbReadTable(mydb, "planes")
weather <- dbReadTable(mydb, "weather")
dbDisconnect(mydb)
```
## Since the flights data base is huge, so I only choose January 1st as my day to import the data.
```{r}
flights <- data.frame(flights)
flights <- flights[flights$month ==1 & flights$day == 1,]
```
## Export the table
```{r}
write.csv(airlines, "~/Desktop/data/airlines.csv", row.names = FALSE)
write.csv(airports, "~/Desktop/data/airports.csv", row.names = FALSE)
write.csv(flights, "~/Desktop/data/flights.csv", row.names = FALSE)
write.csv(planes, "~/Desktop/data/planes.csv", row.names = FALSE)
write.csv(weather, "~/Desktop/data/weather.csv", row.names = FALSE)
```


## Using Neo4j
```{r}
library(RNeo4j)
graph = startGraph("http://localhost:7474/db/data/", username="neo4j", password="081465zN")
clear(graph, input = FALSE)
```

## Node: Airlines
```{r}
addConstraint(graph, "Airline", "carrier")

q1 <- "
CREATE (a:Airline {carrier: {carrier}, name: {name}})
"

t = newTransaction(graph)

for (i in 1:nrow(airlines)) {
  carrier = airlines$carrier[i]
  name = airlines$name[i]

  appendCypher(t, 
               q1, 
               carrier = carrier, 
               name = name)
}

commit(t)
```

##Node: flights
```{r}
q2 <- '
CREATE (b:Flight {name: {name}, carrier: {carrier},  dest: {dest}})
'

t = newTransaction(graph)

for (i in 1:nrow(flights)) {
  name = flights$flight[i]
  carrier = flights$carrier[i]
  origin = flights$origin[i]
  dest = flights$dest[i]

  appendCypher(t, 
               q2, 
               name = name, 
               carrier = carrier,
               dest = dest)
}

commit(t)
```

## Edge Flight and Carrier

```{r}
q3 <- '
MATCH (a:Flight) WHERE a.carrier={carrier} AND a.name={fnum}
MATCH (b:Airline) WHERE b.carrier={carrier}
CREATE (a) -[r:Serves] -> (b)
'

t = newTransaction(graph)

for (i in 1:nrow(flights)) {
  carrier = flights$carrier[i]
  fnum = flights$flight[i]

  appendCypher(t, 
               q3, 
               fnum = fnum,
               carrier = carrier)
}
commit(t)
```

## Conclusions

I am new to Neo4j at the beginning of the project. However, after I did tons of research about Neo4j, I start to like the ways of Neo4j to present the data and relationship between data. Clearly, its advantage is describing relationships between nodes. For analysis, visualizing data is a valuable tool. However, when I am trying to run the database of the flights. If I did not set the date is January 1st, running the entire database of flights seems impossible. It takes a long time to process such a huge data. If I remember correctly about Mysql, it only took a very short period of time to run the entire database. I am still more familiar with the relational database and mysql's language and structure. It provides better data intergrity than NoSQL database. 
Since I learned NoSQL as well. I think I will have more tools help me analyze the data. When I process the huge data, I may need to use Mysql. However, when I want to find and describe the relationship of the data or show the data graphically, I will use NoSQL. 