---
title: "Project 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Player's Seven Round Match Results
Player number, Round Number (1-7), Outcome (W, L, D), Opponent's player number, Opponent's Pre Chess Rating. 

```{r}
library(stringr)
library(knitr)
library(ggplot2)
chess <- readLines("tournamentinfo.txt")
str(chess)
```
## extract information
# We need player's name, player's state, total number of points, player's pre-rating, average pre Chess Rating of Opponents.
```{r}
names <- (str_trim(unlist(str_extract_all(chess, "([[:alpha:] ]-?){15,31}"))))[2:65]
head(names);
states <- str_trim(unlist(str_extract_all(chess, " ON| OH | MI ")))
str(states);
number_points <- unlist(str_extract_all(chess, "[:digit:][//.][:digit:]"))
str(number_points)
prerating <- as.integer(sub(pattern = 'R: ', replacement = '', x = unlist(str_extract_all(chess, "R: [[:digit:] ]{4}"))))
str(prerating)
opponent <- gsub("\\|", " ", str_sub(unlist(str_extract_all(chess, "[:digit:][//.][:digit:][|DLWUXBH[:digit:] ]{44}")), start = 10, end = 47))
str(opponent)
list_opponent <- (strsplit(opponent, " W | D | U | H | B | X | L"))
head(list_opponent)
```
## convert the prerating to a matrix and convert it to integer so that we can calculate the mean
```{r}
matrix1<- sapply(list_opponent, as.numeric)
matrix2 <- matrix(prerating[matrix1], nrow = 7)
average <- as.integer(format(apply(matrix2, 2, mean, na.rm = TRUE), digits= 4))
str(average)
```
## final outcomes
```{r}
final_outcomes <- data.frame(names, states, number_points, prerating, average)
str(final_outcomes)
kable(head(final_outcomes))
difference <- (final_outcomes$prerating - final_outcomes$average)
difference
write.table(final_outcomes, file="chessoutcome.csv", sep=",", row.names= FALSE)
```
