---
title: "Week 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Homework 3 
```{r}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
```
(a). Use the tools of this chapter to rearrange the vector so that all elements conform to the standard firstname last_name.
```{r}
name2 <- sub(" [A-z]{1}\\. "," ",name)
name3 <- sub("(\\w+),\\s(\\w+)","\\2 \\1", name2)
name4 <- sub("[A-z]{2,3}\\. ","",name3)
name4
```
(b). Construct a logical vector indicating whether a character has a title.
```{r}
title <- str_detect(name3,"[A-z]{2,3}\\. ")
df <- data.frame(name3, title)
df
```
(c). Construct a logical vector indicating whether a character has a second name. 
```{r}
secondname <- str_detect(name," [A-z]{1}\\. ")
df <- data.frame(name, secondname)
df
```
4. Describe the tyoes of strings that conform to the following regular expressions and construct an exmaple that is matched by the regular expression.
(a). [0-9]+\\$
One or more numbers followed by $ symbol.
```{r}
library(stringr)
example <- c ("12$", "45$")
str_detect(example, "[0-9]+\\$")
```
(b). \\b[a-z]{1,4}\\b
A word contains 1 to 4 letters.
```{r}
example2 <- c("ok", "four")
str_detect(example2, "\\b[a-z]{1,4}\\b" )
```
(c). .*?\\.txt$
string ends with .txt
```{r}
example3 <- c ("abc.txt", "1.txt")
str_detect(example3,".*?\\.txt$" )
```
(d). \\d{2}/\\d{2}/\\d{4}
numbers have format in nn/nn/nnnn
```{r}
example4 <- c("01/09/1991", "08/14/1965")
str_detect(example4, "\\d{2}/\\d{2}/\\d{4}")
```
(e).<(.+?)>.+?</\\1>
characters inside <> followed by another charater in the <> with / in it.
```{r}
example5 <- c("<tag>Text</tag>")
str_detect(example5, "<(.+?)>.+?</\\1>")
```
9. The following code hides a secret message.
```{r}
secret_message <- paste("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr")
message <- unlist(str_extract_all(secret_message, "[[:upper:].]{1,}"))
message <- str_replace_all(paste(message, collapse = ''), "[.]", " ")
message
```