---
title: "Project2 Professors’ salaries"
author: "Vivian Kong"
date: "October 9, 2016"
output: html_document
---

## (1) Create a .CSV file that includes all of the information above.
The CSV file is saved in the Github.

## (2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy and transform your data.

##(3) Analysis ( I did (2) and (3) together)

```{r}
library(tidyr)
library(dplyr)
require(knitr)
salary1<- read.csv("https://raw.githubusercontent.com/xkong100/IS607/master/Project2/Salaries.csv", stringsAsFactors = FALSE, check.names = FALSE, na.strings = c("", "NA"))
kable(head(salary1))
```

# We want to analyze professors' salary when they service under 20 years.

```{r}
salary1 <- data.frame(salary1[,-4])
salary2 <- salary1 %>% filter(yrs.service <=20)
salary3 <- salary2 %>% arrange(salary)
kable(head(salary3))
salary3 %>% summarise (Mean_salary_under20yrs = mean(salary), min_salary_under20yrs = min(salary), max_salary_under20yrs= max(salary))

```

The mean salary is $108768.8, the minimum salary is $63100, and the maximum salary is $204000 when the professors service under 20 years.


# We also want to find out professor's salary when they service more than 20 years.


```{r}
salary4 <- salary1 %>% filter(yrs.service > 20)
salary5 <- salary4 %>% arrange(salary)
kable(head(salary5))
salary5 %>% summarise (Mean_salary_morethatn20yrs = mean(salary), min_salary_morethan20yrs = min(salary), max_salary_morethan20yrs= max(salary))

```

The mean salary is $122103.9, the minimum salary is $57800, and the maximum salary is $231545 when the professors service more than 20 years.

By comparing the mean salary, we can conclude that, the service time and the salary has positive relationship.


# We also want to find out the relationship between salary and genders.

```{r}
salary6 <- salary1 %>% spread(sex, salary)
salary6$Female[is.na(salary6$Female)] <-0
salary6$Male[is.na(salary6$Male)] <- 0
salary7 <- within(salary6, {Female <- as.numeric(as.character(Female))
Male <-as.numeric(as.character(Male))})
kable(head(salary7))

salary7 %>% summarise (Mean_salary_Female = mean(Female),  max_salary_Female= max(Female),Mean_salary_male=mean(Male), max_salary_male=max(Male))
```

From our analysis, we can conclude that Female's salary is lower than the Male's salary by comparing their mean salaries and max salaries.




