---
title: "Assignment 5"
author: "Vivian Kong"
date: "September 30, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## (1) Create a .CSV file that includes all of the information above.
The CSV file is saved in the Github.

## (2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy and transform your data.

```{r}
library(tidyr)
library(dplyr)
require(knitr)
data <- read.csv("https://raw.githubusercontent.com/xkong100/IS607/master/Assignment-5/Airline.csv", stringsAsFactors = FALSE, check.names = FALSE, na.strings = c("", "NA"))
kable(head(data))
```

# remove the NA in the 3rd row

```{r}
data <- data.frame(data[-3, ])
kable(head(data))
```

# Give name for rows and columns and replace the rows which still have NA 

```{r}
colnames(data)[1]="Airline"
colnames(data)[2]="Status"
data[2,1]="ALASKA"
data[4,1]="AM WEST"
kable(head(data))
```

# Now, we can use "gather" of tidyr to gather the rows and columns

```{r}
tdata <- gather(data, "Destination", "Number_of_time", 3:7)
kable(head(tdata))
```

# spread the "on time" and "delay"

```{r}
tdata1 <- spread(tdata, key= Status, value = Number_of_time)
colnames(tdata1)[4]="ontime"
kable(head(tdata1))
```

## (3) Perform analysis to compare the arrival delays for the two airlines.

# Convert delayed and ontime to numerical value so that it is easy to calculate. 

```{r}
tdata1 <- within(tdata1, {delayed <- as.numeric(as.character(delayed))
ontime <-as.numeric(as.character(ontime))})

# Use "mutate" to preserve the old list but add new columns of "total" and "PercentDelayed"

tdata1<-mutate(tdata1, Total= delayed + ontime, PercentDelayed = delayed / Total*100)
tdata1 <- arrange(tdata1, PercentDelayed)
kable(tdata1)
```

# group and find the average delayed percent by Airlines

```{r}
delays <- tdata1 %>% group_by(Airline) %>% summarise(MeanPercent= round(mean(PercentDelayed, 0)))
delays
```

##Alaska is delayed 19% and AM WEST is 18% of the time.

